Suplementary information: Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-05-03 SupplementaryInformation.tex
Quite los \newpage y unos cambiecillos mas

Many equivalent formulations have been proposed to obtain $\bm M$. For
a periodically
replicated multilayered system, the transfer matrix may be constructed
from the normal modes of the corresponding photonic crystal. These
modes are described by Bloch's
theorem, which reads in this case,
\begin{equation}
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{N}}=\bm M%
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{0}}=e^{\pm iKD}%
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{0}},  \label{Bloch}
\end{equation}%
where $D=z_{N}-z_{0}$ is the period, which corresponds to the actual
thickness of the multilayered system, and $\pm K$ is the 1D Bloch's
vector describing the propagation along $z$. Thus, $\Lambda_{\pm }=e^{\pm iKD}$ are
the eigenvalues of transfer matrix $\bm M$ and $E_{\Vert }^{\pm }$ and $H_{\Vert
}^{\pm }$ are the corresponding eigenvectors. Notice that $\det M=1$  exactly,
so the product of eigenvalues $\Lambda_{+}\Lambda_{-}=1$ and the
dispersion relation of the Bloch modes becomes
\begin{equation}
\cos KD=\frac{1}{2}\text{Tr}\,\bm M  \label{dispersion}
\end{equation}%
where T$\text{r}$ denotes the trace. \begin{figure}[tbph]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SIF1Squeme1DPC.pdf}
	\end{center}
	\caption{(a) Chirped-type photonic structure formed by two alternating
		materials $a$ and $b$, with refractive indices $n_{a}$ and $n_{b}$,
		thickness $d_{a}$ and $d_{b}$ that increases gradually
                according to some design scheme. We show schematically
                the  incident and reflected electric and magnetic
                fields, $\bm E_i$, $\bm H_i$,  $\bm E_r$, $\bm H_r$,
                their wavevectors $\bm k_i$ and $\bm k_r$, the right
                ($+$) and left ($-$) moving fields within each layer
                as well as their wavevectors $\bm k_\alpha^\pm$. (b)
                The multilayer system can be replaced by an
		effective layer within which supports right and left
                moving Bloch waves with wavevectors $\bm K^\pm=(\bm Q,
                \pm K)$ and electric and magnetic field amplitudes
                $\bm E_\beta^\pm$ and $\bm H_\beta$. The projection of
              the wavevector unto the $xy$ plane is $\bm Q$ for all
              the waves, due to translational symmetry and $K$ is
              obtained from Eq. \eqref{dispersion}.}
	\label{Fig1}
\end{figure}

@@

\begin{table}[tbph]
	\caption{Optimized design parameters for different profile
          function classes for different porosity contrasts and some
          properties (number of periods, thickness and average
          reflectance) of the resulting structures.}
	\includegraphics[width=\textwidth]
	{SITableOptimized.pdf}
\end{table}

@@

\begin{figure}[tbph]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SIReflectanceVisNIR.pdf}
	\end{center}
	\caption{Calculated reflectance of the optimized structures
          with profile class $f_{1}$ (left), $f_{2}$
          (center) and $f_{3}$ (right) and with the porosities
          $30\%/76\%$ (upper panels) and $42\%/76\%$ (lower
          panels). The dotted lines limit the area of the ODB.}
	\label{Fig2}
\end{figure}

\newpage

@@

We calclulated the trace of the transfer matrix of single Bragg mirrors formed by one period (Fig.
\ref{Fig3}(a)) and six periods (Fig. \ref{Fig3}(b)), as well as their
corresponding reflectance (Figs. \ref{Fig3}(c)
and \ref{Fig3}(d)), as a function of the design wavelength
$\lambda_{\text{dis}}$ and the wavelength of the illuminating light.
$\text{Tr}\,\bm M$ and $R(\lambda,\theta)$ were calculated for
TE polarized light incident at an angle of $45^\circ$.
Fig. \ref{Fig3}(d) shows that a
6-period mirror tuned to a  wavelength greater than 1000
nm, may also reflect in a certain region of the visible spectrum. Then, to
reinforce the reflection of the electromagnetic waves in the visible
a smaller number of periods is enough. This is another reason for increasing
number of periods in the 400 to 800 nm region.
\begin{figure}[tbph]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SITrazasyRefSE.pdf}
	\end{center}
	\caption{Calculated trace of the transfer matrix (left) and
          reflectance (right) of single Bragg mirrors one (top)
          and six (bottom) periods as a function of the design
          wavelength $\lambda_{\text{dis}}$ and the illumination
          wavelength $\lambda_{\text{ilum}}$.
          The calculations correspond to an incidence angle $\theta=45^\circ$.}
	\label{Fig3}
\end{figure}
\newpage

>>>>

\begin{figure}[!ht]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SIF1Squeme1DPC.pdf}
	\end{center}
	\caption{(a) Chirped-type photonic structure formed by two alternating
		materials $a$ and $b$, with refractive indices $n_{a}$ and $n_{b}$,
		thickness $d_{a}$ and $d_{b}$ that increases gradually
		according to some design scheme. We show schematically
		the  incident and reflected electric and magnetic
		fields, $\bm E_i$, $\bm H_i$,  $\bm E_r$, $\bm H_r$,
		their wavevectors $\bm k_i$ and $\bm k_r$, the right
		($+$) and left ($-$) moving fields within each layer
		as well as their wavevectors $\bm k_\alpha^\pm$. (b)
		The multilayer system can be replaced by an
		effective layer within which supports right and left
		moving Bloch waves with wavevectors $\bm K^\pm=(\bm Q,
		\pm K)$ and electric and magnetic field amplitudes
		$\bm E_\beta^\pm$ and $\bm H_\beta$. The projection of
		the wavevector unto the $xy$ plane is $\bm Q$ for all
		the waves, due to translational symmetry and $K$ is
		obtained from Eq. \eqref{dispersion}.}
	\label{Fig1}
\end{figure}

Many equivalent formulations have been proposed to obtain $\bm M$. For
a periodically
replicated multilayered system, the transfer matrix may be constructed
from the normal modes of the corresponding photonic crystal. These
modes are described by Bloch's
theorem, which reads in this case,
\begin{equation}
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{N}}=\bm M%
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{0}}=e^{\pm iKD}%
\begin{pmatrix}
E_{\Vert }^{\pm } \\
H_{\Vert }^{\pm }%
\end{pmatrix}%
_{z_{0}},  \label{Bloch}
\end{equation}%
where $D=z_{N}-z_{0}$ is the period, which corresponds to the actual
thickness of the multilayered system, and $\pm K$ is the 1D Bloch's
vector describing the propagation along $z$. Thus, $\Lambda_{\pm }=e^{\pm iKD}$ are
the eigenvalues of transfer matrix $\bm M$ and $E_{\Vert }^{\pm }$ and $H_{\Vert
}^{\pm }$ are the corresponding eigenvectors. Notice that $\det M=1$  exactly,
so the product of eigenvalues $\Lambda_{+}\Lambda_{-}=1$ and the
dispersion relation of the Bloch modes becomes
\begin{equation}
\cos KD=\frac{1}{2}\text{Tr}\,\bm M  \label{dispersion}
\end{equation}%
where T$\text{r}$ denotes the trace.

@@

\begin{table}[!ht]
	\caption{Optimized design parameters for different profile
          function classes for different porosity contrasts and some
          properties (number of periods, thickness and average
          reflectance) of the resulting structures.}
	\includegraphics[width=\textwidth]
	{SITableOptimized.pdf}
\end{table}

@@

\begin{figure}[!ht]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SIReflectanceVisNIR.pdf}
	\end{center}
	\caption{Calculated reflectance of the optimized structures
          with profile class $f_{1}$ (left), $f_{2}$
          (center) and $f_{3}$ (right) and with the porosities
          $30\%/76\%$ (upper panels) and $42\%/76\%$ (lower
          panels). The dotted lines limit the area of the ODB.}
	\label{Fig2}
\end{figure}

@@

We calclulated the trace of the transfer matrix of single Bragg mirrors formed by one period (Fig.
\ref{Fig3}(a)) and six periods (Fig. \ref{Fig3}(c)), as well as their
corresponding reflectance (Figs. \ref{Fig3}(b)
and \ref{Fig3}(d)), as a function of the design wavelength
$\lambda_{\text{dis}}$ and the wavelength of the illuminating light.
$\text{Tr}\,\bm M$ and $R(\lambda,\theta)$ were calculated for
TE polarized light incident at an angle of $45^\circ$.
Fig. \ref{Fig3}(d) shows that a
6-period mirror tuned to a  wavelength greater than 1000
nm, may also reflect in a certain region of the visible spectrum. Then, to
reinforce the reflection of the electromagnetic waves in the visible
a smaller number of periods is enough. This is another reason for decreasing
number of periods in the 400 to 800 nm region.
\begin{figure}[!ht]
	\begin{center}
		\includegraphics[width=\textwidth]
		{SITrazasyRefSE.pdf}
	\end{center}
	\caption{Calculated trace of the transfer matrix (top) and
          reflectance (bottom) of single Bragg mirrors one (left)
          and six (right) periods as a function of the design
          wavelength $\lambda_{\text{dis}}$ and the illumination
          wavelength $\lambda_{\text{ilum}}$.
          The calculations correspond to an incidence angle $\theta=45^\circ$.}
	\label{Fig3}
\end{figure}
